\section{七月十八日}
\dailyquote{	Life, after all, is not as good or as bad as we believe it to be. 

人生，并不是意想中的那么好，也不是意想中的那么坏。
}{Guy de Maupassant（莫泊桑） }{happy}
\poem{Oread（山岳女神）}{Hilda Doolittle （西尔达·杜丽特尔）}
{Whirl up, sea---
	
	Whirl your pointed pines, 　　
	
	Splash your great pines,
	
	On our rocks, 　　
	
	Hurl your green over us,
	
	Cover us with your pools of fir.
}{翻腾的大海——

请高举你粗壮的松林，

拍打我的石岩，

请丢置你的绿意，

再用浩瀚的冷杉林，

倾覆我。
}
\words{提醒幸福(Alert to Happiness )}{毕淑敏(Shumin Bi)}{
我们从小就习惯了在提醒中过日子。天气刚有一丝风吹草动，妈妈就说：别忘了多穿衣服；才相识了一个朋友，爸爸就说：小心他是个骗子；取得了一点成功，还没容得乐出声来，所有关切着你的人会一起说：别骄傲；沉浸在欢快中的时候，自己不停地对自己说：千万不可太高兴，苦难也许马上就要降临……我们已经习惯了在提醒中过日子，看得见的恐惧和看不见的恐惧始终像乌鸦盘旋在头顶。

Since we were little, we have been used to going through lives being alerted constantly. At the first sign of a strong wind in the weather, my mother would say: “Don't forget to put on more clothes.” Shortly after meeting a new friend, my father would say: “Be careful he is a swindler.” Before I could voice my joy after a bit of success, all the people who are concerned about you would say: “Don't be cocky.” While I am immersed in ecstasy, I would still say to myself repeatedly: “Don't get too happy. Bad things could descend very soon.” We are used to going through days of being alerted constantly. Apprehensions, both visible and invisible, hover above our heads all the time like crows.

在皓月当空的良宵，提醒会走出来对你说：注意风暴。于是我们忽略了皎洁的月光，急急忙忙做好风暴来临前的一切准备。当我们睁大着眼睛枕戈待旦之时，风暴却像迟归的羊群，不知在哪里徘徊。当我们实在忍受不了等待灾难的煎熬时，我们甚至会恶意地祈盼风暴早些到来。

On a beautiful night under shinning moonlight in the sky, an alert could ring out to you: “Watch for the storm.” So we ignore the shiny moon and hurry to make all preparations for arrival of storm. While we are in wide-eyed high alert for the onslaught, storm could be like a herd of late-returning sheep wandering around somewhere where nobody knows. Sometimes when we could no longer withstand the suspense in waiting for disaster to strike, we may even maliciously wish the storm would come sooner.

风暴终于姗姗地来了。我们怅然发现，所做的准备多半是没有用的。事先能够抵御的风险毕竟有限，世上无法预计的灾难却是无限的。战胜灾难靠的更多的是临门一脚，先前的惴惴不安帮不上忙。

The storm takes its sweet time but finally arrives. Disappointedly we find out over half of our preparations are wasted. After all, risks that can be guarded against in advance are limited in number. Unforeseeable disasters in this world are innumerable. On-the-spot maneuvers are keys to overcoming disasters. Ill-timed worries beforehand won't help.

当风暴的尾巴终于远去，我们守住零乱的家园，气还没有喘匀，新的提醒又智慧地响起来，我们又开始对未来充满恐惧的期待。

When the tail end of the storm is far gone and we are holding on to our shattered homes, new alerts wisely belt out again before we could recover our breath. Once again full-blown dreads about the future start all over again.

人生总是有灾难。其实大多数人早已练就了对灾难的从容，只是还没有学会灾难间隙的快活。我们太多注重了自己警觉苦难，太忽视提醒幸福。请从此注意幸福！幸福也需要提醒吗？

Disaster is part of life. In fact most people have learned to be accommodating to disasters. What they haven't learned is how to have fun between disasters. We are paying too much attention to alert ourselves to disasters, and overlook the importance of reminding ourselves of happiness. Please pay attention to happiness from now on! Is it necessary to be reminded of happiness?

提醒注意跌倒……提醒注意路滑……提醒受骗上当……提醒荣辱不惊……先哲们提醒了我们一万零一次，却不提醒我们幸福。

We have been alerted to falling down, slippery road, victimization to scam, and indifference to ups and downs. Time and time again sages of all eras have alerted us of such mishaps, but they haven't reminded us of happiness.

也许他们认为幸福不提醒也跑不了；也许他们以为好的东西你自会珍惜，犯不上谆谆告诫；也许他们太崇尚血与火，觉得幸福无足挂齿。他们总是站在危崖上，指点我们逃离未来的苦难，但避去苦难之后的时间是什么？

Perhaps they think happiness won't run away even though it has not been reminded. Maybe they think you would automatically cherish a good thing and there is no need to be earnestly cautioned about it. Possibly they revere striking things like blood and fire, and happiness is not worthwhile mentioning. They always stand on the edge of a cliff and direct us on how to escape from future disasters. But then do you know what follows after disasters have dissipated?

那就是幸福啊！

That is happiness.

享受幸福是需要学习的，当幸福即将来临的时刻需要提醒。人可以自然而然地学会感官的享乐，却无法天生地掌握幸福的韵律。灵魂的快意同器官的舒适像一对孪生兄弟，时而相傍相依，时而南辕北辙。

Enjoying happiness needs to be learned, and we ought to be alerted when happiness is imminent. People can naturally learn the pleasures of senses, but are innately unable to grasp the rhythm of happiness. Thrill of soul and contentment of organs are like two peas in a pod which often go hand in hand. Other times they are completely different like night and day.

幸福是一种心灵的振颤，它像会倾听音乐的耳朵一样，需要不断地训练。

Happiness is tremor of the soul. Like an ear that is good at listening to music, it has to be trained continuously.

简言之，幸福就是没有痛苦的时刻，它出现的频率并不像我们想象的那样少。

Simply put, happiness is painless at all times, and its occurrence is not as infrequent as we may imagine.

人们常常只是在幸福的金马车已经驶过去很远，捡起地上的金鬃毛说，原来我见过它。

People often would, after the carriage of happiness is long gone, pick up wisps of mane from the ground and say in fact he has seen it before.

人们喜爱回味幸福的标本，却忽略幸福披着露水散发清香的时刻。那时候我们往往步履匆匆，瞻前顾后不知在忙着什么。

In their penchant for reminiscing happiness at its specimen, they overlook happiness at those moments when it is at its best. At those times often we are hurrying somewhere, looking back and forth and getting busy at God-knows-what.

世上有预报台风的，有预报地震的，没有人预报幸福。其实幸福和世界万物一样，有它的征兆。

In this world, there are predictions on typhoons and earthquakes, but nobody predicts happiness. In fact happiness is much the same as all other things on earth in that there are omens about it.

幸福常常是朦胧的，很有节制地向我们喷洒甘霖。你不要总希冀轰轰烈烈的幸福，它多半只是悄悄地扑面而来；你也不要企图把水龙头拧得更大，使幸福很快地流失，而需静静地以平和之心，体验幸福的真谛。

Happiness often is inconspicuous, and it showers on us in a regulated manner. Don't expect happiness to come in an overwhelming fashion, because mostly it would come in a subtle manner. Also don't turn the faucet of happiness to full blast because it can be exhausted fairly quickly. It is necessary to maintain a calm state of mind in order to appreciate the true essence of happiness.

幸福绝大多数是朴素的，它不会像信号弹似的，在很高的天际闪烁红色的光芒。它披着本色外衣，亲切温暖地包裹起我们。

Happiness in most instances is down-to-earth. It's not like a signal flare which flashes bright red lights high up in the sky. Wearing an inborn-color overcoat, it wraps around us intimately and snugly.

幸福不喜欢喧嚣浮华，常常在暗淡中降临。贫困中相濡以沫的一块糕饼，患难中心心相印的一个眼神，父亲一次粗糙的抚摸，女友一个温馨的字条……这都是千金难买的幸福！像一粒粒缀在旧绸子上的红宝石，在凄凉中愈发熠熠夺目。

A display of rowdiness and glamorization is not favored by happiness, and it descends upon us in a low-key manner. Sharing a meager piece of cake in poverty, exchanging empathetic looks in difficulties, receiving a rough caress from father, and getting a cozy note from girlfriend are all priceless happiness. They are like rubies stitched on old silk fabric in making these dazzling incidents stand out more against a backdrop of desolation.

幸福有时会同我们开一个玩笑，乔装打扮而来，机遇、友情、成功、团圆……它们都酷似幸福，但它们并不等同于幸福。幸福会借了它们的衣裙，袅袅婷婷而来，走得近了，揭去帏幔，才发觉它有钢铁般的内核。幸福有时会很短暂，不像苦难似的笼罩天空。

Sometimes happiness would pull our legs and turn up in disguise. Opportunity, friendship, success, and reunion are happiness look-alikes, but they are not equivalents of happiness. Happiness would borrow their attire and walk over gracefully. When it comes near and takes off its veil, then we would discover it has a steel-like core. Sometimes happiness could be brief, unlike suffering which could be overwhelming as if it were overshadowing the sky.

如果把人生的苦难和幸福分置天平两端，苦难体积庞大，幸福可能只是一块小小的矿石。但指针一定要向幸福这一侧倾斜，因为它有生命的黄金。

If we put life's suffering and happiness on two ends of a scale, then the size of suffering would be a gigantic size and happiness could only be a small piece of mineral rock. However, the indicator would be tilted towards happiness because it contains the gold of life.

幸福有梯形的切面，它可以扩大也可以缩小，就看你是否珍惜。

Happiness has a ladder-shaped plane, and it can be expanded or contracted depending on how well you cherish it.

我们要提高对于幸福的警惕，当它到来的时刻，激情地享受每一分钟。当春天来临的时候，我们要对自己说：这是春天啦！心里就会泛起茸茸的绿意。

We should be on high alert toward happiness. The moment it arrives, we should be all-out in enjoying every minute of it. When spring is here, we must say to ourselves: “This is spring!” Then a feeling of fluffy green would gush out in our minds.

幸福的时候，我们要对自己说：请记住这一刻！幸福就会长久地伴随我们。那我们岂不是拥有了更多的幸福！

At times of happiness, we should say to ourselves: “Please remember this moment!” Then happiness would stay with us for a very long time, and wouldn't we possess more happiness that way?

所以，丰收的季节，先不要去想可能的灾年，我们还有漫长的冬季来得及考虑这件事。我们要和朋友们跳舞唱歌，渲染喜悦。既然种子已经回报了汗水，我们就有权沉浸幸福，不要管以后的风霜雨雪，让我们先把麦子磨成面粉，烘一个香喷喷的面包。

Therefore during bumper harvest season, we shouldn't think first about last year's disastrous crop. We still have a long winter to ponder over this sort of things. We should play up our bliss by dancing and singing with friends. Since seeds have paid back our sweaty efforts, we have the right to indulge ourselves in happiness. Put all those foul weathers that follow out of our mind. Let's grind wheat into flour and bake an appetizing loaf of bread.

所以，当我们从天涯海角相聚在一起的时候，请不要踌躇片刻后的别离。在今后漫长的岁月里，有无数孤寂的夜晚可以独自品尝愁绪。现在的每一分钟，都让它像纯净的酒精，燃烧成幸福的淡蓝色火焰，不留一丝渣滓。让我们一起举杯，说：我们幸福。

Therefore when we chance upon each other at the most unexpected location in this world, don't brood for a moment over the farewell afterwards. In the lingering years to come, there will be countless lonely nights that you could mull over the taste of gloom all by yourself. Let every minute right now flare up to be blue flames of happiness like unadulterated alcohol that burns out without dregs remaining. Also let's toast together and say: “We are blessed with happiness.”

所以，当我们守候在年迈的父母膝下时，哪怕他们鬓发苍苍，哪怕他们垂垂老矣，你都要有勇气对自己说：我很幸福。因为天地无常，总有一天你会失去他们，会无限追悔此刻的时光。

Therefore when we wait around by the feet of our elderly parents, despite their graying and aging, you need to have the courage to say to yourself: “I'm blessed with happiness.” Fate is unpredictable, and one day when you lose your parents you will regret the moments right now.

幸福并不与财富、地位、声望、婚姻同步，这只是你心灵的感觉。

Happiness is not in lockstep with wealth, status, reputation and marriage. It is only a feeling in your mind.

所以，当我们一无所有的时候，我们也能够说：我很幸福，因为我们还有健康的身体；当我们不再享有健康的时候，那些最勇敢的人可以依然微笑着说：我很幸福，因为我还有一颗健康的心；甚至当我们连心也不再存在的时候，那些人类最优秀的分子仍旧可以对宇宙大声说：我很幸福，因为我曾经生活过。

Therefore when we have absolutely nothing, we still could say: “I'm blessed with happiness because I still have my health.” When we are in ill-health, those bravest souls could still smile and say: “I'm blessed with happiness because I still have a healthy heart.” Even when our hearts give out, the most outstanding ones could still say out loud to the universe: “I'm blessed with happiness because I once live a life.”

常常提醒自己注意幸福，就像在寒冷的日子里经常看看太阳，心就会不知不觉的暖洋洋亮光光。

Constantly alerting ourselves to pay attention to happiness is like seeing the sun during cold days by means of which we feel warm and bright inside our hearts unwittingly.
}