 \section{七月二十七日}
 \dailyquote{A novel is a mirror walking along a main road.
 
一部小说犹如一面在大街上走的镜子。
}{Stendhal（司汤达）}{Lotus}
 \poem{Song of a Man Who Has Come Through（身经沧海的男人之歌）}{D.H. Lawrence}{
 	Not I, not I, but the wind that blows through me!
 	
 	A fine wind is blowing the new direction of Time.
 	
 	If only I let it bear me, carry me, if only it carry me!
 	
 	If only I am sensitive, subtle, oh, delicate, a winged gift!
 	
 	If only, most lovely of all, I yield myself and am borrowed
 	
 	By the fine, fine wind that takes its course through the chaos of the world
 	Like a fine, an exquisite chisel, a wedge-blade inserted;
 	
 	If only I am keen and hard like the sheer tip of a wedge
 	
 	Driven by invisible blows,
 	
 	The rock will split, we shall come at the wonder, we shall find the Hesperides.\\
 	
 	
 	Oh, for the wonder that bubbles into my soul,
 	
 	I would be a good fountain, a good well-head,
 	
 	Would blur no whisper, spoil no expression.\\
 	
 	
 	What is the knocking?
 	
 	What is the knocking at the door in the night?
 	
 	It is somebody wants to do us harm.\\
 	
 	
 	No, no, it is the three strange angels.
 	
 	Admit them, admit them}
 {
 不是我，不是我，是风把我穿透！\\
 

柔风送爽，吹动着时光的新方向。\\


如果让它搭上我，带走我，如果它带走我！\\


如果我敏感，精巧，哦，纤巧，是长翅膀的礼物！

如果，最美的是，我屈服于它，\\


让这美之又美的风带我穿过世间的混乱

如同一把精致的錾子，錾头锋利；\\


如果我锐利而坚硬如錾尖\\


让隐形的风驱动，

岩石会凿开，我们会看到奇迹，发现那金苹果园。\\




哦，为了这涌进我灵魂里的奇迹，

我要当一束美好的喷泉，美好的源泉，

不掩饰任何呢喃，不浪费任何表达的语言。\\




哪里来的敲门声？

为什么夜里有敲门声？

是有人要戕害我们。
\\



不，不是，是那三位陌生的天使，

让他们进来，让他们进来。 
}
\poem{纸船——寄母亲(Paper Boats--to Mother)}{冰心(Bing Xin)}
{ 	Never willing to waste a sheet of paper,
	
	I save and save
	
	Then fold them into small, small boats
	
	And throw them into the sea from my ship.
	
	Some are blown back into the portholes,
	
	Others are stuck on the stern, soaked by waves,
	
	And I, undiscouraged, keep on folding and hoping
	
	That one will finally reach its destination.
	
	O Mother, if you ever see a tiny white sail in your dream,
	
	Don't be startled by its unexpected presence for
	
	It was folded by your loving daughter to carry homeward
	
	Across the sea and mountains her love and sorrow.
}{
我从不肯妄弃一张纸，

总是留着——留着

叠成一只只很小的船儿，

从舟上抛下在海里。　

有的被天风吹卷到舟中的窗里，

有的被海浪打湿，沾在船头上。\\


我仍是不灰心的每天叠着，

总希望有一只能流到我要它到的地方去。

母亲，倘若你梦中看见一只很小的白船儿，

不要惊讶它无端入梦。

这是你至爱的女儿含着泪叠的，万水千山，

求它载着她的爱和悲哀归去。

}
 \words{荷叶母亲(The Motherly Lotus Leaf)}{冰心 }{
 父亲的朋友送给我们两缸莲花，一缸是红的，一缸是白的，都摆在院子里。
 
 Recently, my father’s friend gave us two pots of lotus flowers as a gift, which we then placed in our courtyard. In one pot was a red flower, and in the other, a white one.
 
 八年之久，我没有在院子里看莲花了——但故乡的园院里，却有许多；不但有并蒂的，还有三蒂的，四蒂的，都是红莲。
 
 It was eight years since I had seen a lotus flower in our courtyard, but back in our hometown, our garden was full of them: on a single stalk, there might grow two, three or even four flowers; and all were red in color.
 
 九年前的一个月夜，祖父和我在园里乘凉。祖父笑着和我说：“我们园里最初开三蒂莲的时候，正好我们大家庭中添了你们三个姊妹。大家都欢喜，说是应了花瑞。”
 
 On a moonlit night nine years ago, my grandfather and I sat outdoors enjoying the cool air. He smiled and said to me: “The year when you and your sisters were born into our family, three flowers happened to bloom on a single stalk in the garden. We were full of joy, believing the blooming flowers to be an auspicious sign.”
 
 半夜里听见繁杂的雨声，早起是浓阴的天，我觉得有些烦闷。从窗内往外看时，那一朵白莲已经谢了，白瓣儿小船般散飘在水面。梗上只留个小小的莲蓬，和几根淡黄色的花须。那一朵红莲，昨天还是菡萏的，今晨却开满了，亭亭地在绿叶中间立着。
 
 Having been disturbed by the pitter-patter of rain through the night, and seeing an overcast sky when I rose in the morning, I felt a bit annoyed. Looking out of the window, I saw the white flower had already begun to wilt, its petals floating on the surface of the water like little boats. Lingering on the stalk was a small seedpod and a few light yellow stamens. The red flower, which was still in bud last night, was now in full bloom, standing erect among its green leaves.
 
 仍是不适意！——徘徊了一会子，窗外雷声作了，大雨接着就来，愈下愈大。那朵红莲，被那繁密的雨点，打得左右攲斜。在无遮蔽的天空之下，我不敢下阶去，也无法可想。
 
 My feeling of vexation persisted. I paced around the room restlessly before thunder began to roar, followed by rain pelting down. As the raindrops fell more densely, the red lotus flower began to sway from side to side. Nothing under heaven could shield the flower from the rain, and I didn’t dare to run down the steps into the courtyard to do anything for it, nor could I think of any other way to help.
 
 对屋里母亲唤着，我连忙走过去，坐在母亲旁边——一回头忽然看见红莲旁边的一个大荷叶，慢慢地倾侧了下来，正覆盖在红莲上面……我不宁的心绪散尽了！
 
 Hearing my mother’s call from the opposite room, I went to sit by her side and then looked back again towards the red flower. A scene came into view: a huge leaf beside it was tilting over just enough to cover the flower…I felt greatly relieved.
 
 雨势并不减退，红莲却不摇动了。雨点不住地打着，只能在那勇敢慈怜的荷叶上面，聚了些流转无力的水珠。
 
 The rain still refused to let up, but the red flower had a chance to steady itself. The rain continued beating down, but merely formed tiny pools of water rolling harmlessly along the big leaf, which had acted as a protector with love and bravery.
 
 我心中深深地受了感动——
 
 I was touched in the depth of my heart.
 
 母亲啊！你是荷叶，我是红莲。心中的雨点来了，除了你，谁是我在无遮拦天空下的荫蔽？
 
 Dear mother, you are the leaf and I am the flower. Whenever my heart is exposed to a shower of rain, who else can be the one to shield me from the open sky?

}



