 \section{七月二十九日}
 \dailyquote{Marriage is a besieged city. Those outside want to get in and those in the city want to get out.
 
 婚姻是一座围城，城外的人想进去，城里的人想出来。
}{钱钟书}{brute}
 \poems{ 相见欢（ Happy to Meet）}{ 李煜}{0.3\linewidth}{林花谢了春红，
 	
 	太匆匆。
 	
 	无奈朝来寒雨晚来风。\\

 	胭脂泪，
 	
 	相留醉，
 	
 	几时重。
 	
 	自是人生长恨水长东。}{0.7\linewidth}{
  Flowers in the wood shed their blush,
  
 In such a rush.
 
 Helpless, a cold rain at dawn, and a sough at dusk, how drear.\\
 
 What intoxicates one
 
 Is the rouge melting tear.
 
 Could we meet e'er?
 
 For sure, life is a long time grief, a long time eastward flush.
}
 \words{Brute Neighbors（禽兽为邻）}{ Henry David Thoreau}{The mice which haunted my house were not the common ones, which are said to have been introduced into the country, but a wild native kind not found in the village. I sent one to a distinguished naturalist, and it interested him much. When I was building, one of these had its nest underneath the house, and before I had laid the second floor, and swept out the shavings, would come out regularly at lunch time and pick up the crumbs at my feet. It probably had never seen a man before; and it soon became quite familiar, and would run over my shoes and up my clothes. It could readily ascend the sides of the room by short impulses, like a squirrel, which it resembled in its motions. At length, as I leaned with my elbow on the bench one day, it ran up my clothes, and along my sleeve, and round and round the paper which held my dinner, while I kept the latter close, and dodged and played at bo-peep with it; and when at last I held still a piece of cheese between my thumb and finger, it came and nibbled it, sitting in my hand, and afterward cleaned its face and paws, like a fly, and walked away.
 	
 	角逐在我房中的老鼠不是平常的那种；平常的那种据说都是从外面带进此地乡野里来的，可是这种是土生的野鼠，在村子里是找不到的。我寄了一只给一位著名的生物学家，他对它产生了很大的兴趣。在我造这座房子的时候，有一只老鼠就在我的屋子下面做了窝；我楼上的地板还没有铺好，刨花还没有扫出去，每到午饭时分，它就到我脚边来吃面包屑粒。也许它之前从来没有看见过人，我们很快就亲热起来，它奔过我的皮鞋，还爬上我的衣服。它很容易就爬上屋侧，只几窜就上去了——像松鼠，连动作都很相似。到后来，有一天我用手肘支在凳上，它奔上我的衣服，沿着袖子而下，在我盛食物的纸碟边，不断地打转；我把纸碟往身边一拖，不让它走近，一下子又推到它面前去，这样同它耍着玩。最后，我在拇指与食指之间，拈起一块乳酪来，它过来了，坐在我的手掌之中，一口一口地咀嚼。之后，它像苍蝇似的，擦擦脸，又擦擦前掌，扬长而去。
 	
 	A phoebe soon built in my shed, and a robin for protection in a pine which grew against the house. In June the partridge, which is so shy a bird, led her brood past my windows, from the woods in the rear to the front of my house, clucking and calling to them like a hen, and in all her behavior proving herself the hen of the woods. The young suddenly disperse on your approach, at a signal from the mother, as if a whirlwind had swept them away, and they so exactly resemble the dried leaves and twigs that many a traveler has placed his foot in the midst of a brood, and heard the whir of the old bird as she flew off, and her anxious calls and mewing, or seen her trail her wings to attract his attention, without suspecting their neighborhood. The parent will sometimes roll and spin round before you in such a dishabille, that you cannot, for a few moments, detect what kind of creature it is. The young squat still and flat, often running their heads under a leaf, and mind only their mother's directions given from a distance, nor will your approach make them run again and betray themselves. You may even tread on them, or have your eyes on them for a minute, without discovering them. I have held them in my open hand at such a time, and still their only care, obedient to their mother and their instinct, was to squat there without fear or trembling. So perfect is this instinct, that once, when I had laid them on the leaves again, and one accidentally fell on its side, it was found with the rest in exactly the same position ten minutes afterward. They are not callow like the young of most birds, but more perfectly developed and precocious even than chickens. The remarkably adult yet innocent expression of their open and serene eyes is very memorable. All intelligence seems reflected in them. They suggest not merely the purity of infancy, but a wisdom clarified by experience. Such an eye was not born when the bird was, but is coeval with the sky it reflects. The woods do not yield another such a gem. The traveller does not often look into such a limpid well. The ignorant or reckless sportsman often shoots the parent at such a time, and leaves these innocents to fall a prey to some prowling beast or bird, or gradually mingle with the decaying leaves which they so much resemble. It is said that when hatched by a hen they will directly disperse on some alarm, and so are lost, for they never hear the mother's call which gathers them again. These were my hens and chickens.

不久就有一只京燕来我屋上做窠；一只知更鸟在我屋侧的一枝松树上巢居着，求我保护。六月里，鹧鸪这样怕羞的飞鸟也带着她的幼雏飞过我的窗子，从我屋后的林中飞到我的屋前，像一只老母鸡一样，咯咯地唤她的孩子们;从她的行为看来，真像是林中的老母鸡。当你走近了它们，母鸟发一个信号，它们就一哄而散，好像一阵旋风把它们吹走似的。鹧鸪的颜色又很像枯枝败叶，常常有些游客，一脚就踏在鹧鸪的幼雏中间，只见老鸟拍翅飞走，发出焦虑的呼号，扑扑地拍动翅膀，好吸引他的注意--此人怎能想到附近有这么一窠的小鸟呢？母鸟有时羽毛很不整齐地在你面前打滚打旋子，以至你忽然看不出它是什么动物了。幼雏们静静地扁扁地蹲着，常常把头伸在一张叶子底下，什么都不管，只理睬母亲从远处投来的讯号；就是你走近了它们，它们也不奔走，因此也不会被发觉。可能你的脚踩上了它们，眼睛还望了它们一会儿，可你却并未发觉。有一次也是很偶然的，我把它们放在我摊开的掌中，而它们所服从的只是它们的母亲与自己的本能，因此它们只是照旧蹲着，不觉得恐惧，也不打抖。这种本能真是完美之至，我后来把幼雏又放回到树叶上去，有一只不小心侧着跌了下去，可是十分钟之后，我发现它跟别的几只雏鸟一样，在原地好好地蹲着。鹧鸪的幼雏和别种鸟类的幼雏不一样，它们鲜有毛羽不丰满者，它们比别种幼鸟发展得都更为成熟，甚至比雏鸡还要早熟。它们睁大了宁静的眼睛，表情显得很成熟，可是又很天真；你看见了，永远不会忘记。这双眼睛之中似乎反映着一切的知性，它们不仅表现出婴孩期的纯洁，还表示出给经验洗练出来的智慧。这样的眼睛不是鸟儿与生俱来的；它与它所反映的天空成其久远。像它们眼睛一样的宝石，山林里还没有产生过。游客也不常能看到这样一口清澈的井。无知的或是鲁莽的猎人时常在这种时候把母鸟射杀了，使这无辜的一群幼雏成为恶兽猛禽的猎物，或逐渐地混入了那些和它们非常相似的枯叶，同归于尽。据说，这些幼雏要是给一只老母鸡孵出来，它们稍受惊，便一散而走，从此失踪，因为它们听不到母鸟召唤的声音。这些便是我的母鸡和幼雏。

}